InnoDB Full text Search hacking with Shiny/R

### 2015-12-29 article.rmd
comments

```{r init, message = FALSE, echo=FALSE}
#options(width = 9999)
#knitr::opts_chunk$set(width=9999)
# opts_chunk$set(fig.width=9999) #, fig.height=6))

>>>>

```{r init, message = FALSE, echo=FALSE}
library(png)
#options(width = 9999)
knitr::opts_chunk$set(fig.width=9999)
# opts_chunk$set(fig.width=9999) #, fig.height=6))
